\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2021-05-26 paper/jitp_rr_memo/jitp_rr_memo.tex
finished revisions (round 1)

Thank you for your comments and for giving us the opportunity to revise and resubmit our paper Thanks also to the reviewers for their constructive comments. As we hope you will see both in the revised manuscript and in this response letter, we have taken each comment seriously and have endeavored to address each as completely as possible. Each of the comments from reviewers is addressed in the order presented in the review. We do believe that addressing reviewers' comments has significantly improved the paper. \\

@@

    \textbf{Response}:

@@

    \textbf{Response}:

@@

    \textbf{Response}: We

>>>>

Thank you for your comments and for giving us the opportunity to revise and resubmit our paper Thanks also to the reviewers for their constructive comments. As we hope you will see both in the revised manuscript and in this response letter, we have taken each comment seriously and have endeavored to address each as completely as possible. Each of the comments from reviewers is addressed in the order presented in the review. We do believe that addressing reviewers' comments has significantly improved the paper. We should note that we are approximately 450 words over the 5,000 limit for Workbench Notes. We thoroughly trimmed the text to make room for the revisions requested by the reviewers, but would be happy to cut or move additional content to the online appendix if we need to be under the 5,000 limit. \\

@@

    \textbf{Response}: We now recognize that our initial submission jumped right into the estimation and interpretation of differences based on mayoral partisanship, without first discussing why we would expect the priorities of mayors to differ according to party. We added discussion of findings from two recent articles that address how Republican and Democratic mayors differ in terms of policy priorities.

@@

    \textbf{Response}:  Our revised and focused discussion of the scale limitations, and costs, associated with manual web content collection address this point. See also our responses to R2's comments 1--3.

@@

    \textbf{Response}: We have closely proof read the revised manuscript.

### 2021-05-26 paper/manuscript_jitp_rr.tex
finished revisions (round 1)

\section{Introduction} \vspace{-.2cm}
Government websites convey voluminous information about all aspects of government policymaking, policy implementation, and public deliberation. The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites, focusing in particular on textual contents \citep[e.g.,][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra,Eschenfelder2002}. The conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset. Though accurate, the manual approach to data collection is costly for large-scale analysis. We present a methodological pipeline that can be used to automatically scrape government websites in order to build datasets that can be used for text analysis---describing challenges in data collection and processing, as well as the solutions we adopt. We provide an illustrative application in which we explore how the textual contents on city government websites in six American states correlate with the partisanship of the city mayor.

The manual content analysis of government websites is feasible when researchers have access to substantial resources and/or focus their data collection efforts on a small sample of websites.  Consider the example of \citet{Feeney2017}. They analyzed the websites of 500 U.S. municipalities, and recorded information about the sites' coverage of, e.g., the city's social media accounts, the city council agenda, department descriptions, and police reports. To do this, \citet{Feeney2017}, employed two researchers to hand-code each of the 500 websites. If each researcher could complete 5--10 websites per hour, between hours spent on training and data collection, the budget to complete such a project would need to be on the order of thousands of dollars.

Our primary research objective is to introduce a methodological pipeline for government website content extraction that will enable researchers to analyze government website content without incurring the substantial costs associated with manual data collection. Since it is possible to use computer-automated methods to (1) access websites, (2) parse content, and (3) analyze and categorize content, we propose that automated methods can be combined to dramatically lower the cost and increase the scale of projects involving the analysis of government website content. The approach that we propose is a methodological pipeline that can ingest a set of urls that point to government website, and output a corpus of plain text that is extracted from the files available at each URL. The pipeline that we introduce can be used to automatically gather sections of substantive plain text from government websites---covering entire contents including the plain HTML files, and linked files in various formats (e.g., DOC, PDF, and TXT). Our pipeline provides researchers with a highly scalable approach to constructing comprehensive samples of textual data associated with government entities.

@@

The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents. Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, mobile accessibility, and overall function \citep[e.g., ][]{Urban2002,mcneal2003innovating,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}. As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities. The websites of politicians and their parties have also been the object of research \citep{Druckman2009,Druckman2010,cryer2019navigating,Esterling2011,Esterling2011a,Norris2003,Therriault2010}. For example, \cite{Druckman2010} analyze the issues engaged on websites for candidates in U.S. Congressional elections, and find that candidates strategically engage just a few issues based on the priorities in their districts and the characteristics of their opponents.

@@

\vspace{-.2cm}
\section{The Web to Text Pipeline} \vspace{-.2cm}
In this section, we describe our methodological pipeline, with which we take an archive of website files, and output a corpus of formatted plain text documents. We address three methodological challenges.  First, though they contain significant amounts of text, websites are not comprised of clean plain text files. Rather, the files available at websites are of multiple types, including HTML, PDF, word processor, plain text, and image files. The first step is aimed at extracting clean plain text from this heterogeneous file base. The second step in our pipeline is to process the text to remove language that is effective at differentiating one website from another but is uninformative regarding policy or political differences between governments. Finally, these tools need to work consistently across all of the websites in our corpus, in spite of the fact that relevant information is stored and structured in different ways. We make a software recommendation for each of these steps and gather most of them our R package, \texttt{gov2text}. All of the recommended software is either well-established in the natural language processing community, or part of the Unix ecosystem. As such, all of it is free, open source, well-developed and will continue to be supported by a dedicated community. Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling. We will clarify this distinction as we describe steps in our pipeline.

\subsection{Site to Text Conversion}
\subsubsection{File Type Detection}
The format of a file has a major impact on whether and how textual data can be extracted from a document. For the most part, the file type of a document can be correctly determined through the filename ending---its extension. However, there are exceptions to this, which, if ignored, can lead to large amounts of improperly formatted text. For example, we found thousands of documents that ended in .html, when they were actually PDFs. A more accurate test for file type relies on the use of magic numbers, a short sequence of bytes at the start (and sometimes end) of files that is unique for each file type and therefore allows its correct identification. We implement this method using the R package \texttt{wand} \citep{wand}.\footnote{\texttt{Wand} is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which is included in all Linux distributions (which use this library to determine file types by default), Mac OS X, and has also been ported to Windows.}

\subsubsection{Extracting Text from HTML}
The HTML files that websites are comprised of contain a large amount of useful information, but also completely irrelevant text such as menus, navigational elements and other boilerplate. The side-by-side screenshots presented in Figure \ref{fig:garysbs} convey the challenges presented by extracting content for text analysis for websites. The textual content that is substantive and unique to the Gary, IN homepage is the Mayor's message depicted in Figure \ref{fig:garymayor}. The top row of Figure \ref{fig:garysbs} presents the complete homepage, along with all of the text that can be naively extracted from the site. The Mayor's message represents a relatively small fraction of the total text on the page.

@@

\caption{The top image provides a side-by-side depiction of the entire homepage of \url{https://garyin.us/}, accessed on 05/22/2019, and complete/naive extraction of all of the text on the site. Bottom image provides the result of running \url{https://garyin.us/} through the \texttt{boilerpipe} algorithm at \url{https://boilerpipe-web.appspot.com/}.}
\label{fig:garysbs}
\end{figure}

A subfield of the information retrieval literature, dealing with boilerplate extraction, can offer a solution to this problem. The goal of this branch of research is to develop algorithms with the ability to estimate whether a given portion of an HTML file is substantive. To this end, structural features, such as HTML tags (which are not sufficiently informative on their own), text statistics such as word and sentence length, as well as other heuristics are used. We rely on the \texttt{boilerpipe} classifier described in \cite{Kohlschutter2010}, which is implemented through the R package \texttt{boilerpipeR}. The \texttt{boilerpipe} algorithm has been widely used in the computer science and natural language processing literatures, but to our knowledge has not been previously used in the social sciences.   The complete text extracted from the Gary, IN homepage using boilerpipe is depicted in the screenshot in the bottom row of Figure \ref{fig:garysbs}. We see that only the Mayor's message is extracted, leaving the rest of the text as boilerplate.\footnote{In the online appendix we present a replication of the topic modeling presented in the main text below in which we use a minimal HTML parser rather than \texttt{boilerpipe} to process the data. We show that without \texttt{boilerpipe}, some of the most partisan 'topics' are simply website boilerplate text. }

\subsubsection{Extracting Text from PDF, DOC, DOCX and TXT}
The extraction of information from other text-based file formats is more straightforward.\footnote{See \cite{Berg2012} for a discussion of why extracting text from PDFs is nevertheless nontrivial.} To this end, we rely on \texttt{readtext} R package \citep{readtext}, which is a wrapper for a set of parsers.\footnote{\texttt{readtext} determines a document's type solely through its ending---so the conversion described above is necessary.}$^{,}$\footnote{\texttt{readtext} also contains an HTML parser, but it does not eliminate boilerplate like boilerpipe.} The breakdown of all files by type is given in the online appendix. The most frequent file type besides HTML is PDF, from which we are able to extract a substantial amount of usable text. Files of type DOC, TXT, and DOCX, also occur regularly in our corpus and offer a considerable volume of textual data.

\subsection{Preprocessing}
Preprocessing is an important part of text-as-data research and choices made therein can have significant effects on the outcomes of an analysis \citep{denny2018text}. As such, our advice given in this section, more than in any other, is specific to the problem of extracting meaningful textual information from municipal government websites, with the end goal of its use in a bag-of-words-based model. The techniques we employ might also be of use in other types of applications, but by no means should this section be regarded as a general-purpose manual for preprocessing. The challenge in conducting preprocessing for a comparative analysis of websites lies in the considerable variance between websites. Some of it is substantively informative and some of it is completely irrelevant. As an example of the latter, names of city officials and citizen petitioners feature frequently in city documents. The same is true for streets, locations and not least of all, the city itself. Since individual names recur at a much higher rate within a city than across the entire corpus, this would cause a topic model to cluster its topics by city. Consequently we require a tool which detects the signal in the noise and does so consistently for a discordant set of sources.

@@

To this end, we turn to a common method in natural language processing---part-of-speech (POS) tagging and named entity recognition (NER). In our case, names are the source of substantively uninteresting heterogeneity between cities, so NER is used to detect and remove them.\footnote{We retain laws, nationalities or religious or political groups, as well as works of art (e.g., statutes).} However, we caution here that for many other applications, where the names of political actors might be of interest, this step is not recommended. Furthermore, we select words on the basis of their POS-tags, retaining only nouns (the modal category), verbs, and adjectives.\footnote{For applications outside of bag-of-words models, where the grammatical structure remains of interest, users might also want to retain other parts of speech.} Furthermore, we keep proper nouns that also occur as nouns---this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name. Finally, we also conduct lemmatization to reduce words to their basic form.\footnote{Lemmatization is similar to stemming, but works differently by taking grammar and surrounding words into account to identify the dictionary form of a word. } POS-tagging, NER and lemmatization are all implemented through \texttt{spacyr}. To deal with any leftover issues, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell}).  A final and crucial step is the removal of duplicate documents, which occur very frequently on websites. In addition to their primary purpose, the previous preprocessing steps also help in stripping otherwise identical documents of information that makes them unique -- such as names and dates -- thus facilitating their deletion. %The removal of duplicate information also solves a problem posed by a recurring feature of municipal websites -- city calendars. For most days in most cities, these calendars tend to be empty, but nevertheless contain a template, which would lead to the creation of a document in our corpus. These short and repetitive -- but numerous -- texts would pose severe problems to a topic model. Our approach preserves the valuable information contained within these calendars when cities do make use of them, but removes them when they offer no substantive data.

After preprocessing, our corpus consists of 356,911 documents.  In Table \ref{tab:list} we summarize all of the steps we take in gathering and processing our data. The summary includes a brief description of the step, the software packages used, and an indicator of whether the method is implemented in our R package, \texttt{gov2text}. The package is hosted on GitHub at ({\em blinded for anonymity}). We have also created an interactive tutorial, hosted on Google Colab \citep{bisong2019google}, in which we illustrate the use of \texttt{gov2text}.

@@

@@

City mayors use government websites to present their policy priorities to the public. Consider an example; \cite[p.55]{formicola2003faith} document a significant website content change during a transition in mayoral administrations in the city of Indianapolis. Under the Republican mayor Stephen Goldsmith, voluminous content was added to the city website in connection with the Front Porch Alliance---a faith-based initiative to create partnerships with religious organizations for the use and administration of city resources. Faith-based initiatives represent a type of public-private partnership that is popular with Republicans \citep{saperstein2003public}. When Democrat Bart Peterson took office in 2000, the material related to the Front Porch Alliance was removed from the website. We consider whether the partisan manipulation of city website contents documented in this example holds in a large-scale and more recent sample of city websites. We illustrate the analysis of municipal website content by studying the ways in which differences in website content correlate with the partisanship of the city's mayor mayor. As we reviewed above, the partisanship of the mayor has been found in past research to affect several features of city governance. However, \citet{gerber2011mayors} note that, due to the constraints of state and national policies, municipalities lack discretion in many domains of governance. These constraints do not apply to website contents. City governments have great discretion in composing their websites, modifying website content is low cost relative to other policy changes, and, as reviewed above, city websites provide an effective and often-used means of communication with city residents.

@@

To study content differences between government websites based on mayoral partisanship, we draw upon a recently-developed class model for text, the structural topic model (STM), developed by \citet{Roberts2014}. Building on the conception of ``topics'' in conventional topic models \citep{valdez2018topic}, in the STM a topic is a multinomial distribution defined on the word types in the corpus dictionary. The log-odds of the topic probabilities in each document-specific multinomial distribution over topics are drawn from a multivariate normal distribution in which the topic-specific means are determined by a linear regression function that associates document-attributed covariates with topics. For example, in the context of municipal website content, the structural topic model can be used to estimate a regression coefficient that defines the linear relationship between the log-odds of the municipality's population and the log-odds of each topic. For our primary empirical investigation, the STM provides a tool to estimate the relationship between the party of the city's mayor and the prevalence of each topic. We also include the municipality's population and median income as covariates. Further details on and results from our STM specification can be found in the online appendix.

@@

The results are shown in Table \ref{tabSTMtopwords60}. First, it is notable that the 95\% credible interval includes zero in only seven of the sixty topics, indicating that the topics discussed on city websites varies systematically with the partisanship of the mayor. Many of the topics associated with Democrats fit with what we understand to be national party priorities. Topic \textbf{52}, on affordable housing, clearly resonates with the Democratic party's appeal to low-income voters. Topic {\bf 6} ('race', 'islander', 'census, 'female') covers racial and gender identity issues. Similarly, employee rights and benefits are represented in topics \textbf{10} and \textbf{29}. Democrats also exhibit a strong preference for words related to public finances, such as Topic \textbf{58} ('budget', 'revenue', 'expenditure'), Topic {\bf 45} ('asset', 'actuarial', 'liability', 'financial'), Topic \textbf{35} ('bond', 'obligation', 'proceeds') as well as Topic \textbf{55} ('taxable', 'deed', 'value'). We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater willingness to emphasize the city's efforts to raise and spend money, and take credit for those efforts (e.g., the Gary, IN example in Figure \ref{fig:garymayor}). This finding is consistent with \cite{Einstein2015}, who show that Democratic mayors tend to favor greater spending. A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, \textbf{59} ('burglary', 'robbery', 'theft', 'homicide') is clearly focused on crime. On the one hand, Democratic partisans have a more negative perception of the police, rating it considerably more negatively on the appropriate use of force and the equal treatment of minorities \citep{brown2017different}. On the other hand, the literature has also shown that cities with a higher Democratic vote share spend more on law enforcement, even after controlling for crime \citep{Einstein2015}.

City websites with Republican mayors, meanwhile, exhibit a pronounced focus on the essential functions of government. Basic utilities such as energy (Topic \textbf{20}), fire protection (Topic \textbf{51}), vaccination (Topic \textbf{2}),  and sanitation (Topic \textbf{47}), are prevalent among cities with Republican mayors. These basic service topics cannot be found among topics prevalent in cities with Democratic mayors. Similarly, zoning issues figure prominently in the set of republican topic (Topic \textbf{19}), which fits with the findings of \citet{sorens2018effects} that Republicans are more supportive of restrictive residential zoning rules. The Democratic topics also include one that is somewhat focused on zoning, Topic {\bf 39} ('downtown', 'mixed', 'density'), but emphasizes mixed-use zoning---a loosening of conventional single-use zoning rules.

We further interpret the STM results using the visualizations we present in Figure \ref{demreptop}. In this figure we illustrate the difference between Democrat and Republican mayor city documents in terms of the proportion of content predicted to be allocated to the respective topics. We illustrate the topics that are discussed above.  Looking at the Democrat-leaning topics, we see that documents from Democratic mayor cities are approximately 1/2 of a percent more likely to include the affordable housing topic than are documents from Republican mayor cities. This may seem like a small effect, but 1/2 of a percent represents 30\% of the average proportion of content represented by each of the sixty topics in this STM. Looking at the Republican portion of the figure, the proportion of content appearing in documents from Republican mayor cities that is is allocated to the topic on sanitation is approximately 2/3 of a percent higher than in Democratic mayor cities. This represents 40\% of the average proportion of content allocated to a given topic.  To recap these results, the differences in content we find are meaningful both in terms of topics and the sizes of differences based on the partisanship of the city's mayor.

\begin{figure}
\centering
\includegraphics[scale=0.725]{figures/Democratic_topics}\\
\includegraphics[scale=0.725]{figures/Republican_topics} \vspace{-.65cm}
\caption{Topic differences in proportion prevalence between Democrat and Republican mayor city websites. Depicting topics highlighted in discussion. Top plot gives more Democratic topics, and bottom gives more Republican topics.} \vspace{-.3cm}
\label{fig:demreptop}
\end{figure}

@@

We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis. We have produced an R package \texttt{gov2text}, in which we have implemented and wrapped the core components of our pipeline. The key implication of our results is that the methodology we introduce holds the potential to vastly scale up, and lower the cost of, the data collection efforts underpinning the growing body of research that is focused on government website analysis. Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government. We find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.

Above we referenced several research projects that involved the analysis of government websites, and those of politicians or candidates in elections. Our pipeline would be applicable to projects such as these. However, the application of the methods we propose is not limited to government and politician websites. Our pipeline can be used in the context of any project that would benefit from the analysis of textual content from a large population of websites. For example, \citet{coyle2020no} analyze the content of company websites to find manufacturing companies that use contract manufacturing arrangements in their business models. \citet{kluver2015measuring} use the textual content presented on interest group websites to classify the groups' issue agendas and constituencies. There is a broad body of research programs that could make use of the data collection and processing pipeline we present.

The biggest limitation in our pipeline, and an open area for future research, is the reliance on \texttt{wget} to gather the initial website files. By using \texttt{wget}, we miss content that is displayed dynamically on websites using JavaScript. For any one website, it would be possible to customize a routine with \texttt{Selenium} to access dynamic elements, but the process would need to be customized for each website.\footnote{ We investigated whether the presence of JavaScript was related to the amount of text we gathered from the website. We calculated the correlation between the number of <script> HTML tags on a city's website, which indicate the use of JavaScript on a site, and the number of text tokens we scrape from the site. This correlation is -0.059, which indicates a very weak relationship between the use of JavaScript and the amount of text scraped from the site.}

>>>>

\section{Introduction} \vspace{-.2cm}
Government websites convey voluminous information about all aspects of government policymaking, policy implementation, and public deliberation. A substantial body of research has focused on the contents of government websites \citep[e.g.,][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra,Eschenfelder2002}. The conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset. The manual content analysis of government websites is only feasible when researchers have access to substantial resources or focus on a small sample of websites.  Consider the example of \citet{Feeney2017}. They analyzed the websites of 500 U.S. municipalities, and recorded information about the sites' coverage of, e.g., the city's social media accounts, council agenda, department descriptions, and police reports. They employed two researchers to code each of the 500 websites. If each researcher could complete 5--10 websites per hour, between hours spent on training and data collection, the budget to complete such a project would need to be on the order of thousands of dollars.

Our primary research objective is to introduce a methodological pipeline that will enable researchers to gather and analyze government website content without incurring the substantial costs associated with manual data collection. Since it is possible to use computer-automated methods to (1) access websites, (2) parse content, and (3) analyze and categorize content, we propose that automated methods can be combined to dramatically lower the cost and increase the scale of projects involving the analysis of government website content. Our pipeline ingests a set of urls that point to government websites, and outputs a corpus of plain text that is extracted from the files, of all types (e.g., HTML, DOC, PDF, and TXT) available at each URL.

@@

The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents. Research on `e-governance' evaluates government websites in terms of accessibility, ease-of-use, mobile accessibility, and overall function \citep[e.g., ][]{Urban2002,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}. As an example, \cite{grimmelikhuijsen2012developing} study local government websites of Dutch municipalities to measure government transparency regarding air quality in the municipalities. The websites of politicians and their parties have also been the object of research \citep{Druckman2009,cryer2019navigating,Esterling2011,Esterling2011a,Norris2003,Therriault2010}. For example, \cite{Druckman2010} analyze the issues engaged on websites for candidates in U.S. Congressional elections, and find that candidates strategically engage just a few issues based on the priorities in their districts and the characteristics of their opponents.

@@

\vspace{-.2cm}
\section{The Web to Text Pipeline} \vspace{-.2cm}
In this section, we describe our methodological pipeline, with which we take an archive of website files, and output a corpus of formatted plain text documents. We address three methodological challenges.  First, though they contain significant amounts of text, websites are not comprised of clean plain text files. Rather, the files available at websites are of multiple types, including HTML, PDF, word processor, plain text, and image files. The first step is aimed at extracting clean plain text from this heterogeneous file base. The second step in our pipeline is to process the text to remove language that is effective at differentiating one website from another but is substantively uninformative. Finally, these tools need to work consistently across all of the websites in our corpus, in spite of the fact that relevant information is stored and structured in different ways. We make a software recommendation for each of these steps and gather most of them in our R package, \texttt{gov2text}. Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling. We will clarify this distinction as we describe steps in our pipeline.

\subsection{Site to Text Conversion}
\subsubsection{File Type Detection}
The format of a file impacts how textual data can be extracted from a document. For the most part, the file type of a document can be correctly determined its extension. However, there are exceptions to this, which, if ignored, can lead to large amounts of improperly formatted text. For example, we found thousands of documents that ended in .html, when they were actually PDFs. A more accurate test for file type relies on the use of magic numbers, a short sequence of bytes at the start (and sometimes end) of files that is unique for each file type. We implement this method using the R package \texttt{wand} \citep{wand}.%\footnote{\texttt{Wand} is an R interface to the Unix library \texttt{libmagic} \citep{darwin2008libmagic}, which is included in all Linux distributions (which use this library to determine file types by default), Mac OS X, and has also been ported to Windows.}

\subsubsection{Extracting Text from HTML}
The HTML files that websites are comprised of contain a large amount of useful information, but also completely irrelevant text such as menus, navigational elements and other ``boilerplate''. The side-by-side screenshots presented in Figure \ref{fig:garysbs} convey the challenges presented by extracting content for text analysis for websites. The textual content that is substantive and unique to the Gary, IN homepage is the Mayor's message depicted in Figure \ref{fig:garymayor}. The top row of Figure \ref{fig:garysbs} presents the complete homepage, along with all of the text that can be naively extracted from the site. The Mayor's message represents a relatively small fraction of the total text on the page.

@@

\caption{The top image provides a side-by-side depiction of the entire homepage of \url{https://garyin.us/}, accessed on 05/22/2019, and complete/naive extraction of all of the text on the site. Bottom image provides the result of running \url{https://garyin.us/} through \texttt{boilerpipe}.}
\label{fig:garysbs}
\end{figure}

To remove text that does not represent substantive content we rely on the \texttt{boilerpipe} classifier described in \cite{Kohlschutter2010}, which is implemented through the R package \texttt{boilerpipeR}. The \texttt{boilerpipe} algorithm has been widely used in the natural language processing literature, but to our knowledge has not been previously used in the social sciences.   The complete text extracted from the Gary, IN homepage using boilerpipe is depicted in the screenshot in the bottom row of Figure \ref{fig:garysbs}. We see that only the Mayor's message is extracted, leaving the rest of the text as boilerplate.\footnote{In the online appendix we show that without using \texttt{boilerpipe}, some of the most partisan 'topics' are simply website boilerplate text. }

\subsubsection{Extracting Text from PDF, DOC, DOCX and TXT}
The extraction of information from other text-based file formats is more straightforward. To this end, we rely on \texttt{readtext} R package \citep{readtext}, which is a wrapper for a set of parsers.\footnote{\texttt{readtext} determines a document's type solely through its ending---so the conversion described above is necessary.} The breakdown of all files by type is given in the online appendix. The most frequent file type besides HTML is PDF, from which we are able to extract a substantial amount of usable text. Files of type DOC, TXT, and DOCX, also occur regularly in our corpus and offer a considerable volume of textual data.

\subsection{Preprocessing}
Preprocessing is an important part of text-as-data research \citep{denny2018text}. Our advice given in this section, more than in any other, is specific to the problem of extracting meaningful textual information from municipal government websites, with the end goal of its use in a bag-of-words-based model. The challenge in conducting preprocessing for a comparative analysis of websites lies in the considerable, yet substantively irrelevant, differences between websites. For example, names of city officials, streets, and the city itself feature frequently in city documents. Since individual names recur at a much higher rate within a city than across the entire corpus, this would cause a topic model to cluster its topics by city.

@@

To process the text we extract, we turn to a common method in natural language processing---part-of-speech (POS) tagging and named entity recognition (NER) to remove most names.\footnote{We retain laws, nationalities or religious or political groups, and works of art.} For applications where the names of political actors might be of interest, this step is not recommended. Furthermore, we select words on the basis of their POS-tags, retaining only nouns, verbs, and adjectives. We keep proper nouns that also occur as nouns---this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name. Finally, we also conduct lemmatization to reduce words to their basic form.\footnote{Lemmatization is similar to stemming, but works differently by taking grammar and surrounding words into account to identify the dictionary form of a word. } POS-tagging, NER and lemmatization are all implemented through \texttt{spacyr}. To deal with any leftover issues, we remove words with less than three characters, stopwords and non-English words (using the R package \texttt{Hunspell}).  We also remove duplicate documents, which occur very frequently on websites. %In addition to their primary purpose, the previous preprocessing steps also help in stripping otherwise identical documents of information that makes them unique -- such as names and dates -- thus facilitating their deletion. %The removal of duplicate information also solves a problem posed by a recurring feature of municipal websites -- city calendars. For most days in most cities, these calendars tend to be empty, but nevertheless contain a template, which would lead to the creation of a document in our corpus. These short and repetitive -- but numerous -- texts would pose severe problems to a topic model. Our approach preserves the valuable information contained within these calendars when cities do make use of them, but removes them when they offer no substantive data.

After preprocessing, our corpus consists of 356,911 documents.  In Table \ref{tab:list} we summarize all of the steps we take in gathering and processing our data. The summary includes a brief description of the step, the software packages used, and an indicator of whether the method is implemented in our R package, \texttt{gov2text}. The package is hosted on GitHub at ({\em blinded for anonymity}). We have also created an interactive tutorial for texttt{gov2text} hosted on Google Colab \citep{bisong2019google}.

@@

The biggest limitation in our pipeline, and an open area for future research, is the reliance on \texttt{wget} to gather the initial website files. By using \texttt{wget}, we miss content that is displayed dynamically on websites using JavaScript. We investigated whether the presence of JavaScript was related to the amount of text we gathered from the website. We calculated the correlation between the number of <script> HTML tags on a city's website, which indicate the use of JavaScript on a site, and the number of text tokens we scrape from the site. This correlation is -0.059, which indicates a very weak relationship between the use of JavaScript and the amount of text scraped from the site.

@@

The policy priorities of U.S. mayors are shaped in large part by their partisan affiliations. For example, \citet{einstein2018mayors} finds that Democratic mayors are much more likely than Republicans to support municipal-level redistributive policies, and \citet{einstein2021pictures} finds that Democratic mayors are more likely to support city-level policies aimed at addressing racial inequality. City mayors use government websites to present their policy priorities to the public. Consider an example; \cite[p.55]{formicola2003faith} document a significant website content change during a transition in mayoral administrations in the city of Indianapolis. Under the Republican mayor Stephen Goldsmith, voluminous content was added to the city website in connection with a faith-based initiative to create administrative partnerships with religious organizations. Faith-based initiatives represent a type of public-private partnership that is popular with Republicans \citep{saperstein2003public}. When Democrat Bart Peterson took office in 2000, the material related to the faith-based initiative was removed from the website.

We illustrate the analysis of municipal website content by studying how differences in website content correlate with the partisanship of the city's mayor. As we reviewed above, the partisanship of the mayor has been found in past research to affect several features of city governance. However, \citet{gerber2011mayors} note that, due to the constraints of state and national policies, municipalities lack discretion in many domains of governance. These constraints do not apply to website contents. City governments have great discretion in composing their websites, modifying website content is low cost.

@@

To study content differences between government websites based on mayoral partisanship, we draw upon a recently-developed class model for text, the structural topic model (STM), developed by \citet{Roberts2014}. Building on the conception of ``topics'' in conventional topic models \citep{valdez2018topic}, in the STM a topic is a multinomial distribution defined on the word types in the corpus dictionary. The log-odds of the topic probabilities in each document-specific multinomial distribution over topics are drawn from a multivariate normal distribution in which the topic-specific means are determined by a linear regression function that associates document-attributed covariates with topics. For our primary empirical investigation, the STM provides a tool to estimate the relationship between the party of the city's mayor and the prevalence of each topic. We also include the municipality's population and median income as covariates. Further details on and results from our STM specification can be found in the online appendix.

@@

The results are shown in Table \ref{tabSTMtopwords60}. First, it is notable that the 95\% credible interval includes zero in only seven of the sixty topics, indicating that the topics discussed on city websites varies systematically with the partisanship of the mayor. Many of the topics associated with Democrats fit with what we understand to be national party priorities. Topic \textbf{52}, on affordable housing, clearly resonates with the Democratic party's appeal to low-income voters. Topic {\bf 6} ('race', 'islander', 'census, 'female') covers racial and gender identity issues. Similarly, employee rights and benefits are represented in topics \textbf{10} and \textbf{29}. Democrats also exhibit a strong preference for words related to public finances, such as Topic \textbf{58} ('budget', 'revenue', 'expenditure'), Topic {\bf 45} ('asset', 'actuarial', 'liability', 'financial'), Topic \textbf{35} ('bond', 'obligation', 'proceeds') as well as Topic \textbf{55} ('taxable', 'deed', 'value'). We suspect that the association of Democratic mayors with finance-related terms is indicative of a greater emphasis on the city's efforts to raise and spend money, and take credit for those efforts (e.g., the Gary, IN example in Figure \ref{fig:garymayor}). This finding is consistent with \cite{Einstein2015}, who show that Democratic mayors tend to favor greater spending. A second, consistent Democratic focus appears to be law enforcement: The most Democratic topic, \textbf{59} ('burglary', 'robbery', 'theft', 'homicide') is clearly focused on crime. On the one hand, Democratic partisans have a more negative perception of the police, rating it considerably more negatively on the appropriate use of force and the equal treatment of minorities \citep{brown2017different}. On the other hand, the literature has also shown that cities with a higher Democratic vote share spend more on law enforcement, even after controlling for crime \citep{Einstein2015}.

City websites with Republican mayors, meanwhile, exhibit a pronounced focus on the essential functions of government. Basic utilities such as energy (Topic \textbf{20}), fire protection (Topic \textbf{51}), vaccination (Topic \textbf{2}),  and sanitation (Topic \textbf{47}), are prevalent among cities with Republican mayors. These basic service topics cannot be found among topics prevalent in cities with Democratic mayors. Similarly, zoning issues figure prominently in the set of Republican topics (Topic \textbf{19}), which fits with the findings of \citet{sorens2018effects} that Republicans are more supportive of restrictive residential zoning rules. The Democratic topics also include one that is somewhat focused on zoning, Topic {\bf 39} ('downtown', 'mixed', 'density'), but emphasizes mixed-use zoning---a loosening of conventional single-use zoning rules.

We further interpret the STM results using the visualizations we present in Figure \ref{demreptop}. In this figure we illustrate the difference between Democrat and Republican mayor city documents in terms of the proportion of content predicted to be allocated to the respective topics. We illustrate the topics that are discussed above.  Looking at the Democrat-leaning topics, we see that documents from Democratic mayor cities are approximately 1/2 of a percent more likely to include the affordable housing topic than are documents from Republican mayor cities. This may seem like a small effect, but 1/2 of a percent represents 30\% of the average proportion of content represented by each of the sixty topics in this STM. Looking at the Republican portion of the figure, the proportion of content appearing in documents from Republican mayor cities that is is allocated to the topic on sanitation is approximately 2/3 of a percent higher than in Democratic mayor cities. This represents 40\% of the average proportion of content allocated to a given topic.

\begin{figure}
\centering
\includegraphics[scale=0.725]{figures/Democratic_topics}\\
\includegraphics[scale=0.725]{figures/Republican_topics} \vspace{-.65cm}
\caption{Topic differences in proportion prevalence between Democrat and Republican mayor city websites. Depicting topics highlighted in discussion. } \vspace{-.3cm}
\label{fig:demreptop}
\end{figure}

@@

We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis. The key implication of our results is that researchers can use the methods we introduce scale up, and lower the cost of, data collection for projects focused on the comparative analysis of website content. Through an application to the analysis of municipal websites in six different state, we find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.

We have highlighted projects focused on government and politician websites. However, the application of the methods we propose is not limited to government and politician websites. Our pipeline can be used in the context of any project that would benefit from the analysis of textual content from a large population of websites. For example, \citet{coyle2020no} analyze the content of company websites to find manufacturing companies that use contract manufacturing arrangements in their business models. \citet{kluver2015measuring} use the textual content presented on interest group websites to classify the groups' issue agendas and constituencies. There is a broad body of research programs that could make use of the data collection and processing pipeline we present.
